*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-15 Code/Manuscript_O2.Rmd
Minor edits

To Be Entered through PLoSONe system and deleted here Czech Academy of
Science (OP) visiting fellowship supporting DAC work at AlgaTech Canada
Research Chair in Phytoplankton Ecophysiology (DAC) Natural Sciences and
Engineering Research Council of Canada, 'Latitude and Light' (DAC)
Canada Foundation for Innovation (DAC) New Brunswick Foundation for
Innovation (DAC and MS) Rice Graduate Fellowship 2021 and 2022 (MS)

XXX PLOS requires grant numbers XXX

>>>>

To Be Entered through PLoSONe system and deleted here 
Czech Academy of Science (OP) visiting fellowship supporting DAC work at AlgaTech 
Canada Research Chair in Phytoplankton Ecophysiology (DAC), Grant number CRC-2017-00075 
Natural Sciences and Engineering Research Council of Canada, 'Latitude and Light' (DAC)
Canada Foundation for Innovation (DAC) 
New Brunswick Foundation for Innovation (DAC and MS) 
Rice Graduate Fellowship 2021 and 2022 (MS)

The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.
